Untitled

### 2024-11-01 code/manuscript_altanalysis.Rmd
stratified analysis

         # OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
         # OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,

@@

dfc <- dfc %>% 
  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
  mutate(Att.random = ifelse(Att > 0, Att, NA), 
         Distress = ifelse(Altman < 2.6, 1, 0))

@@

@@

df.mt <- dfc %>% 
  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, (Total / Staff))) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
  mutate(dm.rate = dm.rate * 100, 
         htn.rate = htn.rate * 100, 
         pap.rate = pap.rate * 100, 
         crc.rate = crc.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         asthma.rate = asthma.rate * 100, 
         cad.rate = cad.rate * 100, 
         ivd.rate = ivd.rate * 100)

@@

df.temptemp <- df.temptemp %>% 
  group_by(ID) %>% 
  mutate(value_min = min(value, na.rm = TRUE), value_max = max(value, na.rm = TRUE), value_last = last(value, na_rm = TRUE), value_first = first(value, na_rm = TRUE)) %>% 
  mutate(Tx = value - value_min) %>%

@@

set.seed(123)
df.temptemp <- df.temptemp %>% 
  #filter(Year == 2012) %>% 
  mutate(Treat = ifelse(Att > 2009 & value_last - value_first > 0, "Treated", "Control")) %>% 
  mutate(Att.random = ifelse(Treat == "Control", sample(possible.vecs, size = 1, replace = T), Att)) %>% 
  mutate(year.rel = Year - Att.random) %>% 
  mutate(Att = ifelse(Att == 2009, 0, Att))

df.temptemp <- df.temptemp #%>% filter(Att %notin% c(2011))

table(df.temptemp$Att)

@@

df.temptemp %>% 
  filter(Year == 2012) %>% 
  ungroup() %>% 
  mutate(Change = value_last - value_first) %>% 
  select(value_first, Change) %>% 
  table()

@@

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
  #coeffs <- rbind(coeffs, model$coeftable[2,])
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH + UrbanRuralFlag| ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
  coeffs <- rbind(coeffs, model$coeftable[1,])

@@

summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% filter(value_min <= 2), 
              Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))

@@

   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)),
  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

for (k in 1:22){

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t..)

@@

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp:Staff) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:Staff) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
  cbind(core.did.estimates) %>% 
   select(name, `Control_0`, `Control_1`, `Treated_0`, `Treated_1`, Unadjusted, Estimate, `95% CI`, Pr...t..) %>% 
  mutate(`% Change` = round(Estimate / `Treated_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, Pr...t.., `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","p-value", "% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 4))

@@

# es.direct <- did2s(
#   data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) , 
#   yname = "Complexity", 
#   treatment = "Tx",
#   first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
#     second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
#     cluster_var = "ID", 
#   verbose = TRUE)
# 
# 
#  
# cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
#       cbind(Group = "Direct",es.direct$coeftable)) %>% 
#   data.frame() %>% 
#   mutate(estimate = as.numeric(Estimate), 
#          std.error = as.numeric(Std..Error), 
#          YearRel = as.numeric(YearRel)) %>% 
#   filter(abs(YearRel) <= 6) %>% 
#  ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
#

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, ZipHHI, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag) %>% 
  ### DATA ERRORS
  filter(Total.Hours <= 1344.00)

@@

  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011))

@@

@@

es.direct <- did2s(
  data = df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011)) %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
  yname = "Total.Hours", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

es.indirect <- did2s(
  data = df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011)) %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
  yname = "Total.Hours", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

@@

nrow(df.z.dist.plot[df.z.dist.plot$DistToClosestSite < 10,])/nrow(df.z.dist.plot)
hist(df.z.dist.plot$DistToClosestSite, breaks = 50, xlim = c(0, 100))

>>>>

          OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
          OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,

@@

dfc <- dfc %>% 
  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         #Altman = 0.18 * quick_ratio + 0.3 * Profitability/100 + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
  mutate(Att.random = ifelse(Att > 0, Att, NA), 
         Distress = ifelse(Altman < 2.6, 1, 0))

@@

dfc %>% 
  filter(`BHCMIS ID` == "012070")

@@

df.mt <- dfc %>% 
  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)) | Staff < 5, NA, (Total / Staff))) %>% 
  mutate(Complexity = (HIV.prev + Asthma.prev + HeartDisease.prev +  Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + Asthma.care + HeartDisease.care +  Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
  mutate(dm.rate = dm.rate * 100, 
         htn.rate = htn.rate * 100, 
         pap.rate = pap.rate * 100, 
         crc.rate = crc.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         asthma.rate = asthma.rate * 100, 
         cad.rate = cad.rate * 100, 
         ivd.rate = ivd.rate * 100)

df.mt[df.mt$Year >= 2010,]$Complexity <- df.mt[df.mt$Year >= 2010,] %>% 
  select(HIV.prev, Depression.prev, HeartDisease.prev, Diabetes.prev, Hypertension.prev) %>% 
  rowMeans(na.rm = TRUE)

df.mt[df.mt$Year >= 2010,]$Intensity <- df.mt[df.mt$Year >= 2010,] %>% 
  select(HIV.care, Depression.care, HeartDisease.care, Diabetes.care, Hypertension.care) %>% 
  rowMeans(na.rm = TRUE)

@@

df.temptemp <- df.temptemp %>% 
  group_by(ID) %>% 
  mutate(value_min = min(value, na.rm = TRUE), value_max = max(value, na.rm = TRUE), value_last = last(value, na_rm = TRUE), value_first = first(value, na_rm = TRUE)) %>% 
  mutate(Tx = value - value_first) %>%

@@

set.seed(123)
df.temptemp <- df.temptemp %>% 
  #filter(Year == 2012) %>% 
  mutate(Treat = ifelse(Att > 2009 & value_last - value_first > 0 , "Treated", "Control")) %>% 
  mutate(Att.random = ifelse(Treat == "Control", sample(possible.vecs, size = 1, replace = T), Att)) %>% 
  mutate(year.rel = Year - Att.random) %>% 
  mutate(Att = ifelse(value_min == value_max, 0, Att))

df.temptemp <- df.temptemp %>% 
  filter(!(Treat == "Control" & Att == 2009))

@@

df.temptemp %>% 
  filter(Year == 2009) %>% 
  ungroup() %>% 
  select(Treat, value_first, value_last) %>% 
  mutate(Change = value_last - value_first) %>% 
  select(value_first, Change) %>% 
  table()

@@

df.temptemp %>% 
  filter(Year == 2009) %>% 
  ungroup() %>% 
  select(`BHCMIS ID`, ID, Treat, value_first, value_last) %>% 
  mutate(Change = value_last - value_first) %>% 
  filter(Treat == "Control") %>% 
  arrange(desc(Change))

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
  #coeffs <- rbind(coeffs, model$coeftable[2,])
  model <- feols(Outcome ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/1000) ~ Tx*value, cluster = "ID", data = df.temptemptemp)
  coeffs <- rbind(coeffs, model$coeftable[1,])

@@

@@

  outlier.vals <- quantile(df.temptemp$Total, p = c(0.01, 0.99), na.rm = TRUE)
   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Total = ifelse(Total <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Total >= outlier.vals[2], outlier.vals[2], Total))),
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 7) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

for (k in 1:23){

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t..)

@@

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp:Closed) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:Closed) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
  cbind(core.did.estimates) %>% 
   select(name, `Control_0`, `Control_1`, `Treated_0`, `Treated_1`, Unadjusted, Estimate, `95% CI`, Pr...t..) %>% 
  mutate(`% Change` = round(Estimate / `Treated_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, Pr...t.., `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","p-value", "% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 4))

df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% 
  ungroup() %>% 
  filter(!is.na(value)) %>% 
  select(Year, Closed) %>% 
  group_by(Year) %>% 
  summarize(mean(Closed))

## Stratified by Baseline Market Density

coeffs.did.strat <- c(0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0)

for (k in 1:23){

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min==2, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>= 3, 1, 0), ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,], model$coeftable[3,]))

core.did.estimates.strat <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.strat[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(EstimateFirst = round(as.numeric(Estimate), 2), `95% CI First` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(Std..Error), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(Std..Error), 2), sep = "")) %>% 
  mutate(EstimateSecond = round(as.numeric(Estimate.1), 2), `95% CI Second` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(Std..Error.1), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(Std..Error.1), 2), sep = "")) %>% 
  mutate(EstimateMore = round(as.numeric(Estimate.2), 2), `95% CI More` = paste(round(as.numeric(Estimate.2) - 1.96 * as.numeric(Std..Error.2), 2), ", ", round(as.numeric(Estimate.2) + 1.96 * as.numeric(Std..Error.2), 2), sep = "")) %>% 
  select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1, EstimateMore, `95% CI More`, Pr...t...2)

core.did.estimates.strat <- core.did.estimates.strat
rownames(core.did.estimates.strat) <- NULL

core.did.estimates.strat

did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx*as.numeric(value_first)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

@@

es.direct <- did2s(
  data = df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | value_first == 1), 
  yname = "Qcomp", 
  treatment = "Tx",
  first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

es.indirect <- did2s(
  data = df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | value_first >= 2), 
  yname = "Qcomp", 
  treatment = "Tx",
  first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% #mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% 
  filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, ZipHHI, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag) %>% 
  ### DATA ERRORS
  filter(Total.Hours <= 1344.00)

@@

  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2009:2012))

@@

did2s(
      data = df.z.temp2 %>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% left_join(df.temptemp %>% ungroup() %>% select(`BHCMIS ID`, value_min, value_first) %>% unique(), by = c("BHCMIS ID")) 
      %>% filter(Att == 0 | DirectlyTreated == 0), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx*ifelse(value_first==1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_first>=2, 1, 0), ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

es.direct <- did2s(
  data = df.z.temp %>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
  yname = "Sites", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

es.indirect <- did2s(
  data = df.z.temp%>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
  yname = "Sites", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

@@

nrow(df.z.dist.plot[df.z.dist.plot$DistToClosestSite < 16.09,])/nrow(df.z.dist.plot)
hist(df.z.dist.plot$DistToClosestSite, breaks = 50, xlim = c(0, 100))
